---
title: "What MATH4753JASON24 does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What MATH4753JASON24 does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", fig.width = 6, fig.height = 6
)
```

```{r setup}
library(MATH4753JASON24)
```

# Introduction 

This R package is a collection of functions that was collected over the course of MATH 4753 or Applied Statistical Methods. Through this, it will demonstrate how each function works and what will be the result from each of them. 

## myncurve

This function accepts 3 values, mu, sigma, and an a value (or x if you want it to read it that way) which is a data set.

The output will be a list of the values that are inputted into the function, the data set, and a plot showing the area of the data set (through a normal distribution). 

As a result we get this:

```{r}
MATH4753JASON24::myncurve(mu=0,sigma=5,fire)
```

## getmode()

This function basically accepts a vector of values (preferably numerical) and from there gets the most occurring value from the vector. 

Here is a demonstration of it in action:

```{r}
list <- c(2,2,3,4,5,6,7,9)
mode <- MATH4753JASON24::getmode(list)
mode
```

## mycltp

This function can accept many values but it mainly accepts 3 which is the sample size (n), the iterations (iter), and the lambda value (which is default to 10). This function plots a central limit theorem for the poisson distribution. It will show 3 plots one being a histogram with the sample mean, the other being a barplot of y, and the last one being a probability of poisson. 

Here is an example of a central limit theorem with a poisson:

```{r}
MATH4753JASON24::mycltp(n=30,iter=10000,lambda=10)
```


## myplot and myquad

This function was the very first function made in the project and its a simple function that basically will give a result using a quadratic equation with the function only accepting a x value (numerical value). myquad is a similar concept to the myplot one except this time it's with different constants.  

Here is an example as to how it works:

```{r}
x = 5
MATH4753JASON24::myplot(x)

MATH4753JASON24::myquad(x)
```


## maxlikg2

This function accepts two theta values and with it, lfun reads a type of function that the user wants to plot with it defaulting to logbinpois. This function specifically assumes that the user wants the maximum likelihood from a poisson distribution which then this plot outputs a maximum likelihood of the poisson distribution. 

Here is an example: 

```{r}
logbinpois=function(theta1,theta2) log(dbinom(5,size=15,prob=theta1)) + log(dpois(6,lambda=theta2))
MATH4753JASON24::maxlikg2(theta1=seq(0,1,length=1000),theta2=seq(0,10,length=1000),lfun=logbinpois) # gets the sequence between 0 and 1 through 1000 values and theta2 goes from 0 10 with the same length
# One thing to note is that this is the coolest function ever
```

## ntickets

This function solves a problem about the issue on overbooking for flights. This function basically looks for the most optimal tickets to be sold in order to avoid overbooking. This function accepts a N amount of seats in the plane and it accepts a gamma value in which there will be an overbooking and p is the chance of the passenger showing up. This will plot two graphs, one discrete and one continuous and it will give a point at a number in which it is the most optimal to sell those tickets to avoid overbooking. 

Here is an example of it in action:

```{r}
MATH4753JASON24::ntickets(N=200,gamma=0.03,0.90)
```
## mysample
This function a n amount of samples, a iter value (iterations), the a time value in which it would plot. Currently it is defualted at n = 1000, iter = 10, and the time being equal to 0.5. The output of this function will be a animation or basically a time of how the plot is created over time (based on the n, iter, and time values). 

For example: 

```{r}
# Default
result <- MATH4753JASON24::mysample()

# With custom numbers
result <- MATH4753JASON24::mysample(n=100,iter=5,time=0.2)
```

## myboot2

This function reads in a iter value, x value, fun value, alpha value, cx value, and any other values used for the function (...). What this program does is that it reads in the iter value, x value (random set), and from there it determines what type of function (fun) will be displayed for the histogram. The alpha value gives the quantiles and from there anything can be changed such as the x and y label (to describe the plot). The plot will also display the values of the confidence interval, the type of function used, and the x value. 

```{r}
# Lets say I want to use the fire csv file and specifically the distance and I want to know the mean through bootstrap: 
MATH4753JASON24::myboot2(x=fire$DISTANCE,xlab="mean")
```

